\LARGE \bf When Children Teach a Robot to Write: An Autonomous Teachable Humanoid Which Uses Simulated Handwriting

### 2014-12-12 main.tex
Revert "R1 scaffolding conclusion comment"
This reverts commit ff8c0552d5f85ff625d1f4f1d37b20aae701e09a.

\addtolength{\textheight}{-11.2cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

@@

We believe this article introduces three noteworthy contributions: an 
innovative application of artificial intelligence for the learning of 
hand-written letters suitable for educative purposes; a method for a 
commercially affordable humanoid, in particular the {\sc nao} robot, to exhibit
simulated fine motor capabilities; and a working autonomous interaction 
suitable for engaging children in complex human-robot interactions, such as 
teacher-learner social interactions and learning from demonstration.

>>>>

\addtolength{\textheight}{-6.3cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

@@

We believe that this article introduces three noteworthy contributions: an
innovative application of data processing and artificial intelligence for the
learning of hand-written letters suitable for educative purposes; a robotic
system which was able to provide scaffolding for complex human-robot
interactions (teacher-learner social interactions, learning by demonstration,
simulated robotic fine motor skills) during two preliminaries studies; and an
initial experimental investigation of what appears to be a new role for robots
in education.

Specifically, the technical challenges involved in developing a teachable
robotic agent in the context of handwriting which have been addressed in this
work include:

    \item developing capabilities for a robot with limited fine motor
        capabilities, in particular the {\sc nao} robot, to engage in the act of
        handwriting in a way which is believable for interacting with children.
        This is accomplished by leveraging simulated handwriting with a
        synchronised tablet communicating via ROS;

    \item developing an algorithm capable of incorporating user feedback and
        demonstrations in order to adapt artificially generated handwriting
        quality so as to simulate a teachable agent, which has been implemented
        by maintaining a learning algorithm in the parameter space of the
        PCA-based shape models and converging towards the parameters of user
        demonstrations; and

    \item integrating the system into a working interaction suitable for
        engaging children in the learning by teaching paradigm, accomplished by
        fusing the robotic drawing capabilities and the learning algorithm for
        handwritten letters established with a central controller which manages
        the flow of the interaction, turn taking and integration of the
        connected devices.
